The Community Land Model, version 5.1 \\ One-at-a-time Parameter Perturbation Ensemble

### 2023-08-31 ms/ms.tex
overleaf

The process of parameter selection for land  models is challenging on account of the intrinsic complexity of the heterogeneous land surface, the diversity and plasticity of plant and microbial life, and the multiplicity of domains that impact the terrestrial biosphere (e.g, hydrology, cryology, biogeochemistry, physiology, land management, micrometeorology, etc.). The number of model parameters required to represent all the relevant processes is large, and model speeds are relatively slow, presenting a major barrier to robust objective calibration, model interpretation and development \cite{fisher2020,dagon2020}.
Thorough assessment of the parameter sensitivity of land models in a manner that is repeatable, open, and integrated with ongoing code development is desirable but challenging \cite{hourdin2017,balaji2022}. It typically requires extensive computational time,  software engineering, and domain-specific expert scientific knowledge.

@@

The PPE is likewise useful for determining which parameters influence which model processes and where. For example the parameters controlling leaf area index vary significantly by biome (Figure \ref{fig:lai}). Plant hydraulics parameters were the most important in the tropical rain forest, photosynthetic capacity in the boreal forest, and runoff and soil evaporation in the temperate grassland/desert biome. The most influential parameters globally include parameters that were important in each of these three biomes.

@@

There were several barriers to perturbing the full set of CLM5-BGC parameters. First, many parameters had not been officially identified as such. In such cases, we identified hard-coded values, established an appropriate parameter name, and extracted that parameter to the CLM parameter file for easier manipulation. In this experiment we perturbed 193 parameters across a variety of CLM processes (Figure \ref{fig:params}). This is not the full set of CLM parameters, as some processes were not included, such as crop phenology and management. In carrying out this experiment, we have likewise realized that the epistemology of climate model `parameters' is highly nuanced, and that defining the parameters within a given model structure can be somewhat subjective, such that it would be difficult to collate a comprehensive or definitive set of parameters for a model like CLM.

@@

>>>>

The process of parameter selection for land  models is challenging on account of the intrinsic complexity of the heterogeneous land surface, the diversity and plasticity of plant and microbial life, and the multiplicity of domains that impact the terrestrial biosphere (e.g, hydrology, cryosphere, biogeochemistry, physiology, land management, etc.). The number of model parameters required to represent all the relevant processes is large, and model speeds are relatively slow, presenting a major barrier to robust objective calibration, model interpretation and development \cite{fisher2020,dagon2020}.
Thorough assessment of the parameter sensitivity of land models in a manner that is repeatable, open, and integrated with ongoing code development is desirable but challenging \cite{hourdin2017,balaji2022}. It typically requires extensive computational time,  software engineering, and domain-specific expert scientific knowledge.

@@

The PPE is likewise useful for determining which parameters influence which model processes and where. For example the parameters controlling leaf area index vary significantly by biome (Figure \ref{fig:lai}). Plant hydraulics parameters were the most important in the tropical rain forest, photosynthetic capacity in the boreal forest, and runoff and soil evaporation in the temperate grassland/desert biome. The most influential parameters for leaf area index globally include parameters that were important in each of these three biomes.

@@

There were several barriers to perturbing the full set of CLM5-BGC parameters. First, many parameters had not been officially identified as such. In such cases, we identified hard-coded values, established an appropriate parameter name, and extracted that parameter to the CLM parameter file for easier manipulation. Although in this experiment we perturbed a large number of parameters (193) across a variety of CLM processes (Figure \ref{fig:params}), this still does not cover the full set of CLM parameters, as some processes were not included, such as crop phenology and management. In carrying out this experiment, we have likewise realized that the epistemology of climate model `parameters' is highly nuanced, and that defining the parameters within a given model structure can be somewhat subjective, such that it would be difficult to collate a comprehensive or definitive set of parameters for a model like CLM.

@@

Land only caveat? Our PPE is run as land-only simulations, using prescribed atmospheric forcing. This is likely to be adequate for estimating many land surface fluxes and pools, in particular of carbon, but could lead to biased estiamtes of water and energy fluxes, as we know that atmospheric feedbacks to land surface characteristics modify the state of the land surface itself (Laguë et al. 2019). Additional work is planned to leverage this one-at-a-time land-only PPE to quatnify how much, where, and for which processes atmospheric feedbacks are likely to change the land surface state substatnially.
